\Title

### 2023-01-31 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

% !TEX encoding = UTF-8 Unicode
% !TeX TS-program = pdfLaTeX
% !TeX spellcheck = en-US
% !BIB TS-program = bibtex
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8
%
% public
% https://github.com/SpikeAI/pyTERtorch/
% https://www.zotero.org/groups/4776796/fastmotiondetection

@@

% 2023-01-13 decision: Revise
% 
% REVIEWER REPORTS

@@

The human brain has the remarkable property of being able to react at any time, while consuming a reasonable amount of energy, about tens of watts. This system is the result of millions of years of natural selection, and a striking difference between biological neural networks and artificial ones is the representation they use. Convolutional Neural Networks (CNNs), for example, represent information passing from one layer to another as tensors storing visual information densely over the visual topography, while representing different properties in different channels. These networks have been known to mimic many properties of biological systems~\citep{schrimpf_brain-score_2020}, yet, this score does not account for rapidity or energy consumption. On the other hand, information in a large majority of biological neural networks is represented as \emph{spikes}, i.e. prototypical all-or-nothing events whose only parameters are their timing and the address of the neuron that emitted this spike~\citep{paugam-moisy_computing_2012}. While CNNs obtain state-of-the-art performances for some computer vision tasks like image recognition, they do not make use of the dynamics inherent to the way we sense our natural environment. The third generation of artificial neural networks, i.e. Spiking Neural Networks (SNNs), include this temporal dimension in their computations. This new kind of algorithms are interesting for computational neuroscience as they represent a better model of biological neurons. Another class of approaches have designed normative models of SNNs that aim to have applications in machine learning. One of these is the SpikeNet algorithm, which uses a purely temporal approach by encoding information using one spike per neuron~\citep{delorme_spikenet_1999}. Another type of SNN using precise spike timing attempts to determine the structure of the network in order to minimize a cost function. This was implemented in the SpikeProp algorithm~\citep{bohte_error-backpropagation_2002} and has been extended in novel gradient-based methods. The surrogate gradient method is now widely used in methods that attempt to transfer performance from CNNs to SNNs~\citep{zenke_remarkable_2021}. However, the performance of SNNs is still lagging that of firing rate-based networks and the question of the advantage of using spikes in machine learning and computer vision remains open.

@@

The present paper proposes additional experiments on a recent model of spiking neurons with heterogeneous synaptic delays (i.e. time between the arrival of an afferent spike at a specific synapse and the contribution of the associated postsynaptic potential to the neuron's soma). This model was trained to solve a motion detection task on a synthetic event-based dataset. Once trained, its event-driven computations could be reduced drastically through the pruning of synapses, while maintaining top performance for classification. This showed that we may use the precise timing of spikes to enhance neural computations. In the different kernels obtained after training, one could observe spiking motifs linked to the different motion directions

>>>>

% !TEX encoding = UTF-8 Unicode
% !TeX TS-program = pdfLaTeX
% !TeX spellcheck = en-US
% !BIB TS-program = bibtex
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8
%
% Guest Editors:
% 
% Kexin Chen - Department of Cognitive Sciences, University of California, Irvine
% Hirak J. Kashyap - Department of Computer Science, University of California, Irvine
% Jeffrey L. Krichmar - Department of Cognitive Sciences, Department of Computer Science, University of California, Irvine
% Xiumin Li - College of Automation, Chongqing University, Chongqing, China
% 
% Kexin Chen, Hirak Kashyap, Jeffrey Krichmar, Xiumin Li
% NeuroVision Organizing Team
% 
% Kexin Chen <kexinc3@uci.edu>
%
% 
% public
% https://github.com/SpikeAI/pyTERtorch/
% https://www.zotero.org/groups/4776796/fastmotiondetection

@@

% preprint server =  https://www.researchsquare.com/login?redirect=/article/rs-2120999/private/timeline
% 
% 2023-01-13 decision: Revise
% 
% REVIEWER REPORTS

@@

The human brain has the remarkable property of being able to react at any time, while consuming a reasonable amount of energy, about tens of watts. This system is the result of millions of years of natural selection, and a striking difference between biological neural networks and artificial ones is the representation they use. Convolutional Neural Networks (CNNs), for example, represent information passing from one layer to another as tensors storing visual information densely over the visual topography, while representing different properties in different channels. These networks have been known to mimic many properties of biological systems~\citep{schrimpf_brain-score_2020}, yet, this score does not account for rapidity or energy consumption. On the other hand, information in a large majority of biological neural networks is represented as \emph{spikes}, i.e. prototypical all-or-nothing events whose only parameters are their timing and the address of the neuron that emitted this spike~\citep{paugam-moisy_computing_2012}. While CNNs obtain state-of-the-art performances for some computer vision tasks like image recognition, they do not make use of the dynamics inherent to the way we sense our natural environment. The third generation of artificial neural networks, i.e. Spiking Neural Networks (SNNs), include this temporal dimension in their computations. This new kind of algorithms are interesting for computational neuroscience as they represent a better model of biological neurons. Some approaches have designed normative models of SNNs that aim to have applications in machine learning. One of these is the SpikeNet algorithm, which uses a purely temporal approach by encoding information using one spike per neuron~\citep{delorme_spikenet_1999}. Another type of SNN using precise spike timing attempts to determine the structure of the network in order to minimize a cost function. This was implemented in the SpikeProp algorithm~\citep{bohte_error-backpropagation_2002} and has been extended in novel gradient-based methods. The surrogate gradient method is now widely used in methods that attempt to transfer performance from CNNs to SNNs~\citep{zenke_remarkable_2021}. However, the performance of SNNs is still lagging that of firing rate-based networks and the question of the advantage of using spikes in machine learning and computer vision remains open.

@@

The present paper proposes additional experiments on a recent model of spiking neurons with heterogeneous synaptic delays (i.e. time between the arrival of an afferent spike at a specific synapse and the contribution of the associated postsynaptic potential to the neuron's soma)~\cite{}. This model was trained to solve a motion detection task on a synthetic event-based dataset. Once trained, its event-driven computations could be reduced drastically through the pruning of synapses, while maintaining top performance for classification. This showed that we may use the precise timing of spikes to enhance neural computations. In the different kernels obtained after training, one could observe spiking motifs linked to the different motion directions
